method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update methods EMG
I updated the paragraph on EMG

data_EMG$block[data_EMG$trigger == " S 21"] <- "1_view_neu"
data_EMG$block[data_EMG$trigger == " S 22"] <- "2_view_neg"
data_EMG$block[data_EMG$trigger == " S 23"] <- "3_distraction"
data_EMG$block[data_EMG$trigger == " S 24"] <- "4_distancing"
data_EMG$block[data_EMG$trigger == " S 25"] <- "5_suppression"
data_EMG$block[data_EMG$trigger == " S 26"] <- "6_choice"

@@

EMG_view <- data_EMG %>%
  subset(data_EMG$block == "1_view_neu" | data_EMG$block == "2_view_neg")
EMG_view$block <- as.factor(EMG_view$block)

@@

# Bayes Factors
EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "1_view_neu"],
                                                                    y = EMG_view$Corr[EMG_view$block == "2_view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf

@@

colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGCorrView_con[1,1] <- "$View_{neutral} - View_{negative}$"

@@

# figure
FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

@@

# Bayes Factors
EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "1_view_neu"],
                                                                   y = EMG_view$Lev[EMG_view$block == "2_view_neg"],
                                                                   progress = FALSE, paired = TRUE))$bf

@@

colnames(EMGLevView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGLevView_con[1,1] <- "$View_{neutral} - View_{negative}$"

@@

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

# effect of strategy on EMG

EMG_reg <- data_EMG %>%
  subset(data_EMG$block != "1_view_neu" & data_EMG$block != "6_choice")
EMG_reg$block <- as.factor(EMG_reg$block)

# corrugator
EMGCorrReg_aov <- afex::aov_ez(data = EMG_reg,
                              id = "ID",
                              dv = "Corr",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

# compute posthoc tests for within measures
EMGCorrReg_emm <- emmeans::emmeans(EMGCorrReg_aov$aov, specs = "block")

EMGCorrReg_con <- as.data.frame(pairs(EMGCorrReg_emm, adjust = "bonferroni"))

# Bayes Factors
EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                      data = EMG_reg,
                                      progress = FALSE)

EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf)

EMGCorrReg_con <- cbind(EMGCorrReg_con,
                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
                                                     df_error = EMGCorrReg_con$df,
                                                     ci = 0.95),digits = 2))

colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"

# figure
FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

EMGLevReg_aov <- afex::aov_ez(data = EMG_reg,
                              id = "ID",
                              dv = "Lev",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

# compute posthoc tests for within measures
EMGLevReg_emm <- emmeans::emmeans(EMGLevReg_aov$aov, specs = "block")

EMGLevReg_con <- as.data.frame(pairs(EMGLevReg_emm, adjust = "bonferroni"))

# Bayes Factors
EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                      data = EMG_reg,
                                      progress = FALSE)

EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf)

EMGCorrReg_con <- cbind(EMGCorrReg_con,
                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
                                                     df_error = EMGCorrReg_con$df,
                                                     ci = 0.95),digits = 2))

colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"

# figure
FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
The paradigm was written and presented using *Psychopy* [@Peirce2019].
We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages ... <!-- name and reference the main analysis packages, agian for consistentcy with Zerna et al. --> for all our analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->
A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
<!-- Attention! OSF is still private --> 
## 2.1 Ethics information

<!-- So liest es sich in Josephines Ms. und so ähnlich liest es sich in publizierten NHB papers. -->
The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
Prior to testing, written informed consent will be obtained.
Participants will receive 30€ in total or course credit for participation.

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).<!-- This results in two digit numbers, with the last digit being zero. Perhaps use papaja::printnun(x, diguts = 1, gt1 = T) instead, this rounds up to 1 digit, but also only displays one digit (at least I hope so) -->
Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
Yet we found accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level.
<!--JZ: Hast du ED schon als Abkürzung eingeführt?--> The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG <!-- Has abbrev. EMG already are been introduced? -->being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

@@

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
<!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ... +3), the relaiability of the measures. -->
### 2.3.2 Emotion regulation paradigm

@@

### 2.3.4 Electromyography

Two bipolar electromyograph (EMG) measures will be recorded in the region of the *corrugator supercilii* and the *levator labii* using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel will be used.
Data will be sampled at 1000 Hz.
To measure *corrugator EMG*, electrodes will be applied to the abraded and cleaned skin on the left *corrugator supercilii*, and to measure *levator EMG*, electrodes were applied in the region of the *levator labii*.
The ground electrode will be placed at the left *Mastoid*.
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Afterwards, the signals will be rectified and segmented.
EMG data will be baseline-corrected to -200 ms to 0 ms to stimulus onset.
Last, the sampling rate is changed to 100 Hz and the AUC for the interval of 6000 ms stimulus presentation extracted for every stimulus.
<!-- Liebe @Anne, habe das aus dem Analyzer zusammengefasst, stimmt das? -- -->

@@

*Effects of emotion regulation on arousal and effort* <br> To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*.
<!-- @Anne please check! =) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
<!-- @Anne please check! =) --> To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
Greenhouse-Geisser-corrected $p$-values and degrees of freedom were reported when assumption of sphericity was violated.
Proportion of explained variance $\eta_{p}^{2}$ was reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.

>>>>

data_EMG$block[data_EMG$trigger == " S 21"] <- "view_neu"
data_EMG$block[data_EMG$trigger == " S 22"] <- "view_neg"
data_EMG$block[data_EMG$trigger == " S 23"] <- "distraction"
data_EMG$block[data_EMG$trigger == " S 24"] <- "distancing"
data_EMG$block[data_EMG$trigger == " S 25"] <- "suppression"
data_EMG$block[data_EMG$trigger == " S 26"] <- "choice"

@@

EMG_view <- data_EMG %>%
  subset(data_EMG$block == "view_neu" | data_EMG$block == "view_neg")
EMG_view$block <- as.factor(EMG_view$block)

@@

# Bayes Factors
EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "view_neu"],
                                                                    y = EMG_view$Corr[EMG_view$block == "view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf

@@

colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGCorrView_con[1,1] <- "$View_{negative} - View_{neutral}$"

@@

# figure
FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

@@

# Bayes Factors
EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "view_neu"],
                                                                    y = EMG_view$Lev[EMG_view$block == "view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf

@@

colnames(EMGLevView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGLevView_con[1,1] <- "$View_{negative} - View_{neutral}$"

@@

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

@@

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
A complete list of all measures assessed in the study will be found at the OSF (<https://osf.io/vnj8x/>) and GitHub (github.com/ChScheffel/COG-ER-ED).
<!-- Attention! OSF is still private --> All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

## 2.1 Ethics information

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).
Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
Yet we found accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level.
<!--JZ: Hast du ED schon als Abkürzung eingeführt?--> The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG are being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

@@

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].

### 2.3.2 Emotion regulation paradigm

@@

### 2.3.4 Facial electromyography

Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence (Bradley & Lang, 2000).
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986).
The ground electrode will be placed over the left *Mastoid*.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 kΩ. 
Data will be sampled at 1000 Hz, filtered, rectified and integrated. 
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presenation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset (cf. Bradley & Lang, 2000). 
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
<!-- AG: insert references -->

@@

*Effects of emotion regulation on arousal and effort* <br> To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*.
<!-- @Anne please check! =) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine 
<!-- AG: hier ein Check!-->
the effects of ER strategies on the emotional facial reaction.
<!-- @Anne please check! =) --> To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
Greenhouse-Geisser-corrected $p$-values and degrees of freedom were reported when assumption of sphericity was violated.
Proportion of explained variance $\eta_{p}^{2}$ was reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
